---
title: "Survey Carbon Data"
author: "Paula"
date: "2024-11-26"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load data
pel <- read.csv("Pelagics.csv")
dem <- read.csv("Demersal_color.csv")

# packages
library(ggplot2)
library(forcats)
theme_set(theme_classic())
library(ggridges)
library(viridis)
```

# Paper figures 

Sampling was conducted aboard the _R/V Celtic Explorer_, during IGFS leg 2 and 3 from November to December 2024.  
Fish were dead after the haul and the samples were taken after. 
Strip method, where pressure is applied along the ventral side of the fish, from the gut to the anus (Windell et al., 1978, Martin MS). 
Dissecting the lower part of the gut and squeezing the faecal material out. 

## Sinking rate

Sinking rate was measured on the boat.Sinking rates were determined for x individual faecal matter aboard ship under calm sea state using a cylinder of 30 cm and a stopwatch. The cylinder was marked with color tape to set the water level, the start of the measuring (10 cm) and the end of the measurement (25 cm). Faecal matter was photographed in a Petry dish with sea water and then it was released and timed while falling a distance of 15 cm. The cylinder was filled with _in situ_ sea water and the temperature of the cylinder did not change over the course of the sinking rate experiment.  

The graduated cylinder was place on a flat surface and filled with in situ sea water. The sinking rate over 15 cm was measured. The samples were allowed to sink for at least 10 cm before initiating the measurement.When samples broke into two or more pieces, the descent of the larger piece was 
measured.

We measure the seconds per 15 cm with was estimate the sinking rate in $m\ d^{-1}$. 

$$w\ (m\ d^{-1}) = \frac{1}{X\ sec} 15\ cm \frac{1\ m}{100\ cm} \frac{86400\ sec}{1\ day} $$


### Remineralisation Length Scale RLS (m)

$$Z = w/k$$
where $w$ is the sinking rate of particle ($m\ d^{-1}$) and $k$ is the turnover rate of POC ($d^{-1}$). 

```{r, include = FALSE}
dem$Sinkrate <- 1/dem$Seconds*(15*86400/100)
pel$Sinkrate <- 1/pel$Seconds*(15*86400/100)
```


### Tables

||Haddock|Whiting|Atlantic Cod|Hake|
|--------|-----------------------|----------------------------|-----------------------|----------------------------|
|Mean(SD)|`r round(mean(dem[dem$Species == "HAD", "Sinkrate"], na.rm = TRUE),0)`(`r round(sd(dem[dem$Species == "HAD", "Sinkrate"], na.rm = TRUE), 0)`)|`r round(mean(dem[dem$Species == "WHG", "Sinkrate"], na.rm = TRUE),0)`(`r round(sd(dem[dem$Species == "WHG", "Sinkrate"], na.rm = TRUE), 0)`)|`r round(mean(dem[dem$Species == "COD", "Sinkrate"], na.rm = TRUE),0)`(`r round(sd(dem[dem$Species == "COD", "Sinkrate"], na.rm = TRUE), 0)`)|`r round(mean(dem[dem$Species == "HKE", "Sinkrate"], na.rm = TRUE),0)`(`r round(sd(dem[dem$Species == "HAKE", "Sinkrate"], na.rm = TRUE), 0)`)|
|Range|`r round(range(dem[dem$Species == "HAD", "Sinkrate"], na.rm = TRUE)[1], 0)`-`r round(range(dem[dem$Species == "HAD", "Sinkrate"], na.rm = TRUE)[2], 0)`|`r round(range(dem[dem$Species == "WHG", "Sinkrate"], na.rm = TRUE)[1], 0)`-`r round(range(dem[dem$Species == "WHG", "Sinkrate"], na.rm = TRUE)[2], 0)`|`r round(range(dem[dem$Species == "COD", "Sinkrate"], na.rm = TRUE)[1], 0)`-`r round(range(dem[dem$Species == "COD", "Sinkrate"], na.rm = TRUE)[2], 0)`|`r round(range(dem[dem$Species == "HKE", "Sinkrate"], na.rm = TRUE)[1], 0)`-`r round(range(dem[dem$Species == "HKE", "Sinkrate"], na.rm = TRUE)[2], 0)`|


||Sprat|Pilchard|Mackarel|Horse mackarel|Blue whiting|Herring|
|--------|---------|------------|-----------|------------|--------------|-----------|
|Mean(SD)|`r round(mean(pel[pel$Species == "SPR", "Sinkrate"]),0)`(`r round(sd(pel[pel$Species == "SPR", "Sinkrate"]), 0)`)|`r round(mean(pel[pel$Species == "PIL", "Sinkrate"]),0)`(`r round(sd(pel[pel$Species == "PIL", "Sinkrate"]), 0)`)|`r round(mean(pel[pel$Species == "MAC", "Sinkrate"]),0)`(`r round(sd(pel[pel$Species == "MAC", "Sinkrate"]), 0)`)|`r round(mean(pel[pel$Species == "HOM", "Sinkrate"]),0)`(`r round(sd(pel[pel$Species == "HOM", "Sinkrate"]), 0)`)|`r round(mean(pel[pel$Species == "WHB", "Sinkrate"]),0)`(`r round(sd(pel[pel$Species == "WHB", "Sinkrate"]), 0)`)|`r round(mean(pel[pel$Species == "HER", "Sinkrate"]),0)`(`r round(sd(pel[pel$Species == "HER", "Sinkrate"]), 0)`)|
|Range| `r round(range(pel[pel$Species == "SPR", "Sinkrate"])[1], 0)`-`r round(range(pel[pel$Species == "SPR", "Sinkrate"])[2], 0)`|`r round(range(pel[pel$Species == "PIL", "Sinkrate"])[1], 0)`-`r round(range(pel[pel$Species == "PIL", "Sinkrate"])[2], 0)`|`r round(range(pel[pel$Species == "MAC", "Sinkrate"])[1], 0)`-`r round(range(pel[pel$Species == "MAC", "Sinkrate"])[2], 0)`|`r round(range(pel[pel$Species == "HOM", "Sinkrate"])[1], 0)`-`r round(range(pel[pel$Species == "HOM", "Sinkrate"])[2], 0)`|`r round(range(pel[pel$Species == "WHB", "Sinkrate"])[1], 0)`-`r round(range(pel[pel$Species == "WHB", "Sinkrate"])[2], 0)`|`r round(range(pel[pel$Species == "HER", "Sinkrate"])[1], 0)`-`r round(range(pel[pel$Species == "HER", "Sinkrate"])[2], 0)`|


## Plot sinking rates

```{r, fig.width = 10, warning = FALSE}
#library(viridis)
#viridis(10, option = "H")
common <- c("CollectorID", "Haul", "Species", "Seconds", "Sinkrate")
data_all <- rbind(dem[, common],pel[,colnames(pel) %in% common])

range(data_all$Sinkrate, na.rm = TRUE)

ggplot(data_all, aes(x = Sinkrate, y = fct_reorder(Species, Sinkrate), fill = fct_reorder(Species, Sinkrate), color = fct_reorder(Species, Sinkrate)))+
  geom_boxplot(alpha = .7)+
  #geom_density_ridges(alpha = .75)+  
  scale_fill_viridis_d(option = "turbo")+
  scale_color_viridis_d(option = "turbo")+
  theme(legend.position = "")+
  labs(y = "")

## Information data
info <- read.csv("stocks_info.csv")
data_info <-merge(data_all, info)


## Haul data
hh <- read.csv("Station_data.csv")
hh <- subset(hh, fldCruiseName == "IGFS2024", select = c("fldCruiseName","fldShotDepth", "fldCruiseStationNumber", "fldStratum"))
hh$Haul <- hh$fldCruiseStationNumber
library(stringr)
hh$Area <- sub("([a-z]+)[A-Z].*", "\\1", hh$fldStratum)


data_info <- merge(data_info, hh)

```

# Density plots of sinking rates per species

```{r}
## Ridges plot
ggplot(data_info, aes(x = Sinkrate, y = fct_reorder(Name, Sinkrate, "mean"), fill = fct_reorder(Name, Sinkrate, "mean"), color = fct_reorder(Name, Sinkrate, "mean")))+
  #geom_boxplot(alpha = .4)+
  geom_density_ridges(alpha = .75)+  
  scale_fill_viridis_d(option = "turbo")+
  scale_color_viridis_d(option = "turbo")+
  theme(legend.position = "")+
  labs(y = "", x = "Sinking rate (m/d)")

ggplot(data_info, aes(x = Sinkrate, y = fct_reorder(Name, Sinkrate, mean), fill = fct_reorder(Name, Sinkrate, mean), color = fct_reorder(Name, Sinkrate, mean)))+
  geom_boxplot( alpha = .65, width = .3)+
  #geom_boxplot(alpha = .1, colour = "black", fill = "white", position = "dodge")+
  geom_density_ridges(alpha = .5)+  
  scale_fill_viridis_d(option = "turbo")+
  scale_color_viridis_d(option = "turbo")+
  theme(legend.position = "")+
  labs(y = "", x = "Sinking rate (m/d)")
```




## Differences between sinking rates

The p-value is lower than the usual threshold of 0.05. You are confident to say there is a statistical difference between the groups. 

```{r}
# Test homogeneity of variances
library(car)
# Test homogeneity of variances
bartlett.test(Sinkrate~Species, data_info) # pvalue<0.05 - not all the groups have the same variance
# Test equality of variances
leveneTest(Sinkrate~Species, data_info)# pvalue<0.05 - differences in sample variances

# Test normal
by(data_info$Sinkrate , data_info$Species, shapiro.test) # had,hke and hke are not normally distributed
hist(data_info$Sinkrate)
shapiro.test(data_info$Sinkrate) # Data is not normal

#########-----------------------------###########
# For non Normal
kruskal.test(Sinkrate~Species, data_info) # there is significant difference between the groups p <0.05
# posthoc
library(FSA)
dunnTest(Sinkrate~Species, data_info, method = "bonferroni")

#########------------------------------############
# ANOVA - for normal and equal variances
anova<- aov(Sinkrate~Species, data_info)
summary(anova)
# posthoc
TukeyHSD(anova)
# ANOVA - for normal and equal variances
anova<- aov(Sinkrate~FeedingGuild, data_info)
summary(anova)
# posthoc
TukeyHSD(anova)
# ANOVA - for normal and equal variances
anova<- aov(Sinkrate~Area, data_info)
summary(anova)
# posthoc
TukeyHSD(anova)
```


### Sinking rate plot vs length
```{r}
ggplot(data = subset(dem, Species %in% c("HAD", "WHG", "HKE", "COD")), mapping = aes(Size, Sinkrate, fill = Species, colour = Species))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(values = c("#FABA39FF" ,"#F66B19FF", "#CB2A04FF", "#7A0403FF"),  labels = c("Hake", "Whiting", "Haddock", "Cod"))+
  scale_fill_manual(values = c( "#FABA39FF" ,"#F66B19FF", "#CB2A04FF", "#7A0403FF"),  labels = c("Hake", "Whiting", "Haddock", "Cod"))+
  labs(y = "Sinking rate (m/d)", x = "Fish length (cm)", col = "Species")

```
Correlation sinking rate with length of the fish. 

```{r}
cordata <- subset(dem, Species %in% c("HAD", "WHG", "HKE", "COD"))
cordata <- subset(dem, Species %in% c("HAD"))
cor(cordata$Size, cordata$Sinkrate, use = "complete.obs")
cor.test(cordata$Size, cordata$Sinkrate, method = "pearson")
## Week relationship significant only for haddock
```

### Model sinking rate

```{r}
ggplot(data = data_info, mapping = aes(FeedingGuild, Sinkrate, fill = FeedingGuild, colour = FeedingGuild))+
  geom_boxplot(alpha = 0.7)+
  geom_point(color = "black")+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")
ggplot(data = data_info, mapping = aes(fldStratum, Sinkrate, fill = fldStratum, colour = fldStratum))+
  geom_boxplot(alpha = 0.7)+
  geom_point(color = "black")+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")

ggplot(data = data_info, mapping = aes(Area, Sinkrate, fill = Area, colour = Area))+
  geom_boxplot(alpha = 0.7)+
  geom_point(color = "black")+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")
```

Test looks like except generalist planktivore, and zooplanktivore all the rest are significantly different. Piscivore, specialist bentivore and (gp and Z).

```{r}
# Test homogeneity of variances
# Test homogeneity of variances
bartlett.test(Sinkrate~FeedingGuild, data_info) # pvalue<0.05 - not all the groups have the same variance
# Test equality of variances
leveneTest(Sinkrate~FeedingGuild, data_info)# pvalue<0.05 - differences in sample variances

# Test normal
by(data_info$Sinkrate , data_info$FeedingGuild, shapiro.test) # had,hke and hke are not normally distributed
hist(data_info$Sinkrate)
shapiro.test(data_info$Sinkrate) # Data is not normal

#########-----------------------------###########
# For non Normal
kruskal.test(Sinkrate~FeedingGuild, data_info) # there is significant difference between the groups p <0.05
# posthoc
library(FSA)
dunnTest(Sinkrate~FeedingGuild, data_info, method = "bonferroni")

#########------------------------------############
# ANOVA - for normal and equal variances
anova<- aov(Sinkrate~FeedingGuild, data_info)
summary(anova)
# posthoc
TukeyHSD(anova)
```
```{r}
data_eff<-data_info[!is.na(data_info$Sinkrate),]

ggplot( data_eff, mapping = aes(fct_reorder(FeedingGuild, Sinkrate, "mean"), Sinkrate))+
  geom_jitter(aes(color = fct_reorder(Species, Sinkrate, "mean")))+
  geom_boxplot(color = "grey", fill = "grey", alpha = .6)+
  scale_color_viridis_d(option = "turbo")+
  coord_flip()+
  labs(x = "", y = "Sinking rate m/d", color = "")

ggplot( data_eff, mapping = aes(fct_reorder(SizeGuild2, Sinkrate, "mean"), Sinkrate))+
  geom_jitter(aes(color = fct_reorder(Species, Sinkrate, "mean")))+
  geom_boxplot(color = "grey", fill = "grey", alpha = .6)+
  scale_color_viridis_d(option = "turbo")+
  coord_flip()+
  labs(x = "", y = "Sinking rate m/d", color = "")
```




```{r}
library(lme4)

m_species <- glmer( Sinkrate~ Species + (1|Haul),
                   data = data_eff,
                   family = Gamma(link="log"),
                   control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5)))
m_feeding <- glmer(Sinkrate ~ FeedingGuild + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5)))

m_sizeFG <- glmer(Sinkrate ~  SizeGuild2 + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5)))

m_size <- glmer(Sinkrate ~   Size + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5)))

m_stratum <- glmer(Sinkrate ~ fldStratum + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e9))) ###

m_area <- glmer(Sinkrate ~ Area + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5)))

m_depth <- glmer(Sinkrate ~ fldShotDepth + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e9))) ####

m_tl <- glmer(Sinkrate ~ Tropic_level + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5))) ####

m_diet <- glmer(Sinkrate ~ Piscivore+GeneralistPlanktivore+Zooplanktivore+SpecialistBenthivore + (1|Haul),
                  data = data_eff,
                  family = Gamma(link="log"),
                  control = glmerControl(optimizer = "bobyqa",
                         optCtrl = list(maxfun = 1e5)))

AIC(m_species, m_feeding,m_sizeFG, m_stratum, m_size, m_area, m_depth, m_diet, m_tl)

summary(m_sizeFG)

AIC(m_species, m_feeding,m_sizeFG, m_stratum, m_size)

```
```{r}
coef_df <- data.frame(Species = names(fixef(m_species)[-1]),
                      Estimate = fixef(m_species)[-1])
ggplot(coef_df, aes(x = Species, y = Estimate)) +
  geom_col() +
  coord_flip() +
  labs(title = "Species-level fixed effects on sinking rate",
       y = "Estimate (log scale)", x = "")
```


```{r}
ggplot(data = data_info, mapping = aes(SizeGuild2, Sinkrate, fill = SizeGuild2, colour = SizeGuild2))+
  geom_boxplot(alpha = 0.7)+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")
```



```{r}
summary(m_species)
library(vegan)
adonis2(data_eff$Sinkrate ~ data_eff$Species, data = data_eff, permutations = 999)

```



#########################################################
## Sinking rate effects


Diet and whatever,...

```{r}
library(reshape2)

dietp <- read.csv("./Diet_Data_Thompson/diet_proportions.csv")
diet <- dcast(dietp, Latin~prey_funcgrp, value.var = "propw")

diet[is.na(diet)] <- 0
info <- merge(info, diet)
```



```{r}
library(reshape2)
vard <- c("Name", "fish", "benthos", "zooplankton", "other", "nekton")
dietdata <- info[, names(info) %in% vard]
#dietdata<-dietdata[!is.na(dietdata$Benthos),]

dietdata <- melt(dietdata, id.vars = c("Name"))
dietdata$`Prey weight` <- as.numeric(dietdata$value)

ggplot(dietdata, aes(fct_relevel(variable, c("fish", "benthos",  "other","zooplankton", "neckton")), fct_relevel(Name, c("Sprat", "Pilchard","Horse mackerel",  "Mackerel",  "Blue whiting", "Herring", "Hake", "Whiting",  "Haddock","Cod")), fill = `Prey weight`))+
  geom_tile()+
  scale_fill_gradient2(mid = "#00a38c", midpoint = .5,low =  "white",  high = "#004d57", na.value = "black",labels = scales::percent)+
  labs( y = "", x = "Prey functional group")
```




```{r, fig.height=10, fig.width=20}
library(gbm)

datamodel <- data_eff[,-c(1:4)]

datamodel$Fish <- as.numeric(datamodel$Fish)
var <- c("Name", "FisheriesGild", "Guild", "SizeGuild2","SizeGuild", "TrophicGuild", "MainDiet", "Diet", "FeedingGuild")
datamodel[, colnames(datamodel) %in% var] <-lapply(datamodel[, colnames(datamodel) %in% var], as.factor)

#varmodel <- c("Sinkrate"  , "Name", "FisheriesGild","SizeGuild2", "TrophicGuild" , "LM", "TL_patel"   ,"Tropic.level" ,  "Diet"  , "FeedingGuild" ,"Fish",  "Benthos",  "Zooplankton", "Other", "Necton")
#datamodel <- datamodel[, colnames(datamodel) %in% var] 

gbm_model <- gbm(
  formula = Sinkrate ~ ., 
  data = datamodel, 
  distribution = "gaussian", 
  n.trees = 5000, 
  interaction.depth = 4, 
  shrinkage = 0.01,
  cv.folds = 5)


summary(gbm_model, las = 1)
plot(gbm_model) 
```



```{r}
data_eff$Fish<-as.numeric(data_eff$Fish) 
lmod <- lm(data = data_eff, Sinkrate~LM+Diet+Fish+Benthos+Necton)
lmod <- lm(data = data_eff, Sinkrate~LM+Benthos)

lmod <- lm(data = data_eff, Sinkrate~LM+FeedingGuild)
summary(lmod)
plot(lmod)

hist(data_eff$Sinkrate)

mod <- glm(data = data_eff, Sinkrate~FeedingGuild, family = "Gamma")
plot(mod)
summary(mod)
```


```{r}
ggplot(data = data_info, mapping = aes(FeedingGuild, Sinkrate, fill = FeedingGuild, colour = FeedingGuild))+
  geom_boxplot(alpha = 0.7)+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")
ggplot(data = data_info, mapping = aes(TrophicGuild, Sinkrate, fill = FisheriesGild, colour = FisheriesGild))+
  geom_boxplot(alpha = 0.7)+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")
ggplot(data = data_info, mapping = aes(MainDiet, Sinkrate, fill = MainDiet, colour = MainDiet))+
  geom_boxplot(alpha = 0.7)+
  geom_violin(alpha = 0.7)+
  theme(legend.position = "")+
  labs(x = "", y = "Sinking rate m/d")
```
```{r}
ggplot(data = data_info, mapping = aes(LM, Sinkrate))+
  geom_point(aes(colour = Species))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")
ggplot(data = data_info, mapping = aes(LM, Sinkrate))+
  geom_point(aes(colour = MainDiet))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")

ggplot(data = data_info, mapping = aes(LM, Sinkrate))+
  geom_point(aes(colour = FisheriesGild))+
  #geom_boxplot(aes(colour = Species))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")

ggplot(data = data_info, mapping = aes(Tropic.level, Sinkrate))+
  geom_point(aes(colour = FisheriesGild))+
  #geom_boxplot(aes(colour = Species))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")
```
```{r}
ggplot(data = data_info, mapping = aes(LM, Sinkrate))+
  geom_point(aes(shape = FisheriesGild, colour = MainDiet))+
  #geom_boxplot(aes(colour = Species))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")
```
Sinking rate of the pellet is lower for pagic fish and higher for demersal fish. 

```{r}
ggplot(data = data_info, mapping = aes(LM, Sinkrate, group.by = FisheriesGild, colour = FisheriesGild))+
  geom_point(aes(colour = MainDiet))+
  #geom_boxplot(aes(colour = Species))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")
```

```{r}
ggplot(data = data_info, mapping = aes(LM, Sinkrate, group.by = MainDiet, colour = MainDiet))+
  geom_point(aes(colour = MainDiet))+
  #geom_boxplot(aes(colour = Species))+
  geom_smooth(method = "lm")+
  labs(x = "", y = "Sinking rate m/d")
```

### Models


```{r}
lmod.sp <- lm(data = data_eff, Sinkrate~Name)
summary(lmod.sp)
plot(lmod.sp)

lmod.fg <- lm(data = data_eff, Sinkrate~FeedingGuild)
summary(lmod.fg)
plot(lmod.fg)

lmod.size <- lm(data = data_eff, Sinkrate~Size)
summary(lmod.size)
plot(lmod.size)

lmod.sizeg <- lm(data = data_eff, Sinkrate~SizeGuild)
summary(lmod.sizeg)
plot(lmod.sizeg)

lmod.sizefg <- lm(data = data_eff, Sinkrate~SizeGuild2)
summary(lmod.sizefg)
plot(lmod.sizefg)

lmod.area <- lm(data = data_eff, Sinkrate~Area)
summary(lmod.area)
plot(lmod.area)

lmod.stratum <- lm(data = data_eff, Sinkrate~fldStratum)
summary(lmod.stratum)
plot(lmod.stratum)

lmod.d <- lm(data = data_eff, Sinkrate~fldShotDepth)
summary(lmod.d)
plot(lmod.d)

lmod.diet <- lm(data = data_eff, Sinkrate~Piscivore+GeneralistPlanktivore+Zooplanktivore+SpecialistBenthivore)
summary(lmod.diet)
plot(lmod.diet)

lmod.dietsize <- lm(data = data_eff, Sinkrate~FeedingGuild+Size)
summary(lmod.dietsize)
plot(lmod.dietsize)

AIC(lmod.sp,lmod.fg,lmod.size, lmod.area, lmod.stratum, lmod.d, lmod.sizeg, lmod.sizefg, lmod.diet, lmod.dietsize)

```


```{r}
hist(data_eff$Sinkrate)

mod1<- glm(data = data_eff, Sinkrate~Name, family = inverse.gaussian(link="log"))
plot(mod1)
summary(mod1)


mod2 <- glm(data = data_eff, Sinkrate~ SizeGuild2, family = inverse.gaussian(link="log"))
plot(mod2)
summary(mod2)


mod3 <- glm(data = data_eff, Sinkrate~Area, family = inverse.gaussian(link="log"))
plot(mod3)
summary(mod3)

AIC(mod1, mod2, mod3)

```
```{r}
hist(data_eff$Sinkrate)

mod.sp<- glm(data = data_eff, Sinkrate~Name, family = Gamma(link="log"))
plot(mod.sp)
summary(mod.sp)


mod.sg2 <- glm(data = data_eff, Sinkrate~ SizeGuild2, family = Gamma(link="log"))
plot(mod.sg2)
summary(mod.sg2)

mod.size <- glm(data = data_eff, Sinkrate~ Size, family = Gamma(link="log"))
plot(mod.size)
summary(mod.size)

mod.fg <- glm(data = data_eff, Sinkrate~ FeedingGuild, family = Gamma(link="log"))
plot(mod.fg)
summary(mod.fg)

mod.fishg <- glm(data = data_eff, Sinkrate~ FisheriesGild, family = Gamma(link="log"))
plot(mod.fishg)
summary(mod.fishg)

mod.depth<- glm(data = data_eff, Sinkrate~fldShotDepth, family = Gamma(link="log"))
plot(mod.depth)
summary(mod.depth)

mod.diet<- glm(data = data_eff, Sinkrate~Piscivore+GeneralistPlanktivore+Zooplanktivore+SpecialistBenthivore, family = Gamma(link="log"))
plot(mod.diet)
summary(mod.diet)

mod.area <- glm(data = data_eff, Sinkrate~Area, family = Gamma(link="log"))
plot(mod.area)
summary(mod.area)

mod.stratum <- glm(data = data_eff, Sinkrate~fldStratum, family = Gamma(link="log"))
plot(mod.stratum)
summary(mod.stratum)

AIC(mod.sp, mod.sg2,mod.size, mod.fg,mod.fishg, mod.area,mod.depth, mod.stratum, mod.diet)
```

```{r}
library(lme4)
m_species <- lmer(Sinkrate ~ Name + (1|Haul), data = data_eff)

m_groups  <- lmer(Sinkrate ~ FeedingGuild + (1|Haul), data = data_eff)
m_fs  <- lmer(Sinkrate ~ fldStratum + (1|Haul), data = data_eff)
m_sg  <- lmer(Sinkrate ~ SizeGuild2 + (1|Haul), data = data_eff)
m_size  <- lmer(Sinkrate ~ Size + (1|Haul), data = data_eff)

AIC(m_species, m_sg, m_groups, m_fs, m_fisheries, m_size)


library(emmeans)
emmeans(m_species, "Name")
```